Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massively Distributed Evolutionary Computation

### 2015-07-30 volunteer-clouds-ieee-ci-si.tex
Completed sentence by @mariosky

Recent works propose the use of cloud computing services for the components of 
client-server distributed EAs. Cloud resources 
can reduce operational costs by outsourcing both hardware and software maintenance 
to the cloud provider. Another advantage is that they enable the provisioning of computing resources beyond what 
is available in most laboratories, allowing researches to 
scale algorithms at reasonable costs. Researchers have proposed the use of 
public clouds such as Amazon EC2 \cite{CloudScale}, Google App Engine\cite{di2013towards} 
and DropBox~\cite{DBLP:conf/cec/ArenasGMCRL11}. The use of JavaScript to implement server side components, 
gives software developers certain advantages in the cloud paradigm. JavaScript is a first-class citizen
in most Platforms as a Service (PaaS) as many support the nodejs framework. Also many web services
have native JavaScript libraries and use JSON for data interchange. Another advantage is that 
Developers can use the same software tools for both client and server side development.
%Ayuda con la mini conclusion
%In this work JavaScript was used in the full stack, some percieved advantages are discussed?
%The proposed software has the advantage of full stack JavaScript development..

>>>>

Recent works propose the use of cloud computing services for the components of 
client-server distributed EAs. Cloud resources 
can reduce operational costs by outsourcing both hardware and software maintenance 
to the cloud provider. Another advantage is that they enable the provisioning of computing resources beyond what 
is available in most laboratories, allowing researches to 
scale algorithms at reasonable costs. Researchers have proposed the use of 
public clouds such as Amazon EC2 \cite{CloudScale}, Google App Engine\cite{di2013towards} 
and DropBox~\cite{DBLP:conf/cec/ArenasGMCRL11}. The use of JavaScript to implement server side components, 
gives software developers certain advantages in the cloud paradigm. JavaScript is a first-class citizen
in most Platforms as a Service (PaaS) as many support the nodejs framework. Also many web services
have native JavaScript libraries and use JSON for data interchange. Another advantage is that 
Developers can use the same software tools for both client and server side development.
%Ayuda con la mini conclusion

In the work presented in this paper, JavaScript was used in the full
stack, which has the advantage of using the same code for writing
desktop or command line and browser clients, both based in the EC
library NodEO \cite{DBLP:conf/gecco/GuervosVGES14}. This saves time when writing code and leverages
expertise acquired in the library itself. 
%The proposed software has the advantage of full stack JavaScript
%development..
